test nonparam

### 2015-02-20 tests/test_nonparam.Rmd
update example

Now try VB to avoid overfitting?
```{r}
res.VB=ash(betahat,betahatsd,g=guni,randomstart=TRUE,VB = TRUE,prior=rep(1,K)) 
res.VB2=ash(betahat,betahatsd,g=guni,randomstart=TRUE,VB = TRUE,prior=rep(1/2,K)) 
res.VB3=ash(betahat,betahatsd,g=guni,randomstart=TRUE,VB = TRUE,prior=rep(1/K,K))

@@

>>>>

Now try VB to avoid overfitting?
```{r cache=TRUE}
res.VB=ash(betahat,betahatsd,g=guni,randomstart=TRUE,VB = TRUE,prior=rep(1,K)) 
res.VB2=ash(betahat,betahatsd,g=guni,randomstart=TRUE,VB = TRUE,prior=rep(1/2,K)) 
res.VB3=ash(betahat,betahatsd,g=guni,randomstart=TRUE,VB = TRUE,prior=rep(1/K,K))

@@

Try same thing with less noise
```{r}
set.seed(100)
# First, try fixing g to a true g (but not unimodal)
beta = c(rnorm(1000,0,1),rnorm(1000,5,1))
betahatsd = 0.05
betahat = rnorm(length(beta),mean=beta,sd=betahatsd)
g = normalmix(c(0.5,0.5),c(0,5),c(1,1))
res.1=ash(betahat,betahatsd,g=g,control=list(maxiter=0)) # use the mixture components in g, and also the mixture proportions since don't iterate!
res.2=ash(betahat,betahatsd,g=g) # use the mixture components in g, but iterate!
```
